Data Prep: IUCN and AquaMaps

### 2016-02-16 data_explore/data_prep.Rmd
updates

library(rgbif)
# library(robis)

system.time({
  x <- occ_search(scientificName = spp_all$sciname[1:100], fields = 'minimal', limit = 1)
  ### seems linear - 10 names ~ 2.5 sec, 100 names ~ 25 sec, 1000 names, ~250 sec
  ### so 30000 names ~ 7500 sec or 2 hours
})
y <- sapply(x, function(x) x$meta$count)
gbif_occur <- data.frame(sciname = names(y), gbif_occ = y)

gbif_occur <- gbif_occur %>% 
  left_join(spp_all %>%
              select(iucn_sid, am_sid, sciname),
            by = 'sciname') %>%
  left_join(read_csv(file.path(dir_data_remote, 'aquamaps/v2015/csv/speciesoccursum.csv')) %>%
                       select(am_sid = speciesid, occurcells),
                     by = 'am_sid')

@@

write_csv(gbif_occur, file.path(dir_data, 'gbif_occurrence_df.csv'))

source('obis_count.R')
scinames <- spp_all$sciname[1:100]

@@

write_csv(obis_occur, file.path(dir_data, 'obis_occurrence_df.csv'))

>>>>

library(rgbif)

# system.time({
#   x <- occ_search(scientificName = spp_all$sciname[1:100], fields = 'minimal', limit = 1)
#   ### seems linear - 10 names ~ 2.5 sec, 100 names ~ 25 sec, 1000 names, ~250 sec
#   ### so 30000 names ~ 7500 sec or 2 hours
# })
# y <- sapply(x, function(x) x$meta$count)
# gbif_occur <- data.frame(sciname = names(y), gbif_occ = y)
# 
# gbif_occur <- gbif_occur %>% 
#   left_join(spp_all %>%
#               select(iucn_sid, am_sid, sciname),
#             by = 'sciname') %>%
#   left_join(read_csv(file.path(dir_data_remote, 'aquamaps/v2015/csv/speciesoccursum.csv')) %>%
#                        select(am_sid = speciesid, occurcells),
#                      by = 'am_sid')

@@

# write_csv(gbif_occur, file.path(dir_data, 'gbif_occurrence_df.csv'))
gbif_occur <- read_csv(file.path(dir_data, 'gbif_occurrence_df.csv'))

source('obis_count.R')
scinames <- spp_all$sciname

@@

write_csv(obis_occur, file.path(dir_data, 'obis_occurrence.csv'))
